Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-10-05 Manuscript/manuscript.tex
Corrected DHDMA formula, changed APL tables, added extra APls in SI.

\subsubsection{Simulations of POPC bilayers with cationic surfactants}
An automated topology builder \cite{malde11} was first used to create the structure of
dihexadecyldimethylammonium \\[0.5cm]
%\vspace{0.5cm}
\chemfig{
 -[:0,3.5,,,draw=none]\chemabove{N}{\scriptstyle\oplus} (-[:135]H_3C)(-[:225]H_3C)(-[:315]{(}CH2{)}_{16}-CH_3)(-[:45]{(}CH2{)}_{16}-CH_3)
} , 
\vspace{0.5cm} \\
which is one of the cationic surfactants used to experimentally quantify the electrometer concept~\cite{scherer89}.
The AmberTools program \cite{amber} was then used to generate the Amber-type force field
parameters. The parameters were converted to the Gromacs format by using
the acpype tool \cite{acpype}. The partial charges were then manually modified
to approximately correspond to their equivalent segments in Lipid14 \cite{dickson14}.
The surfactants were randomly placed among the lipids to form bilayer structures with
mole fractions of 10\%, 20\%, 30\%, 42\%, or 50\% of surfactant in the POPC bilayer.
All systems contained 50 POPC molecules per leaflet, 6340 TIP3P water molecules and
6, 14, 21, 35, or 50 surfactants per leaflet. Chloride counter ions were used
in simulations, because parameters for bromide, which was used in the experiment \cite{scherer89},
were not available in the standard Gromacs files for Amber force field.
The systems were simulated for 200~ns using Lipid14 model for POPC where reasonable lipid neighbor exchange occurs.
First 20~ns were omitted from the analysis.

@@

\begin{table}
  \caption{Area per lipid (APL) from different models of POPC without ions\label{tab:apls} }
  \begin{tabular}{l|c c}
    model          & APL (\AA$^2$)   & Temperature [K] \\
    \hline
    Lipid14 \cite{dickson14}  & 65.6$\pm$ 0.5  &  303 \\
    \hline
    ECC-lipids &        &  \\
    %Lipid14ecc0.80+sigma0.875 &        &  313    \\
    ($4.6\cdot 5.1 \, \mathrm{nm}^2$), 72 lipids patch, OPC3           & 63.2   &   313      \\
    \hline
    (6.4 nm)$^2$, 128 lipids patch, OPC3           & 64.2   &  313       \\
    (6.4 nm)$^2$, 128 lipids patch, SPC/E          & 65.1   &  313       \\
    (6.4 nm)$^2$, 128 lipids patch, OPC            & 64.4   &  313       \\
    (6.4 nm)$^2$, 128 lipids patch, TIP4p/2005     & 66.8   &  313       \\
    %($9.2\cdot 10.2 \, \mathrm{nm}^2$), 288 lipids patch           & 65.5   &  313       \\ %% not done for this model with f_sigma=0.89
    %oMM small patch           & 63.65  &         \\
    %oMM 4xbig patch           & 63.7   &         \\
    \hline
    %experiment   & 62.7  &  293    \\
    experiment \cite{jambeck12}\todoii{REF}{put original references, not Slipids param. paper.} & 64.3  &  303    \\
    experiment  & 67.3  &  323    \\
    %experiment  & 68.1  &  333    \\
    %experiment POPE  & 56.6 &  303    \\
    \hline
  \end{tabular}
  \todo{SAMULI: I would put here Lipid14 in 303K, ECC-lipid in 303K and experiment in 303K. Rest in SI.
  The best experimental value would be the one analyzed from the form factor shown in previous figure, 
  if available.}
\end{table}

@@

>>>>

\subsubsection{Simulations of POPC bilayers with cationic surfactants}
An automated topology builder \cite{malde11} was first used to create the structure of
dihexadecyldimethylammonium \\[0.5cm]
%\vspace{0.5cm}
\chemfig{
 -[:0,3.5,,,draw=none]\chemabove{N}{\scriptstyle\oplus} (-[:150]H_3C)(-[:210]H_3C)(-[:330]{(}CH2{)}_{15}-CH_3)(-[:30]{(}CH2{)}_{15}-CH_3)
} , 
\vspace{0.5cm} \\
which is one of the cationic surfactants used to experimentally quantify the electrometer concept~\cite{scherer89}.
The AmberTools program \cite{amber} was then used to generate the Amber-type force field
parameters. The parameters were converted to the Gromacs format by using
the acpype tool \cite{acpype}. The partial charges were then manually modified
to approximately correspond to their equivalent segments in Lipid14 \cite{dickson14}.
The surfactants were randomly placed among the lipids to form bilayer structures with
mole fractions of 10\%, 20\%, 30\%, 42\%, or 50\% of surfactant in the POPC bilayer.
All systems contained 50 POPC molecules per leaflet, 6340 TIP3P water molecules and
6, 14, 21, 35, or 50 surfactants per leaflet. 
%Chloride counter ions were used
%in simulations, because parameters for bromide, which was used in the experiment \cite{scherer89},
%were not available in the standard Gromacs files for Amber force field.
The systems were simulated for 200~ns using Lipid14 model for POPC where reasonable lipid neighbor exchange occurs.
First 20~ns were omitted from the analysis.

@@

\begin{table}
  \caption{Area per lipid (APL) from different models of POPC with no ions\label{tab:apls} }
  \begin{tabular}{l|c c}
    model          & APL (\AA$^2$)   & Temperature [K] \\
    \hline
    Lipid14                   & 65.1$\pm$ 0.6  &  300 \\
    Lipid14 \cite{dickson14}  & 65.6$\pm$ 0.5  &  303 \\
    \hline
    ECC-lipids                & 62.2$\pm$ 0.6  &  300       \\
    \hline
    experiment \cite{jambeck12}\todoii{REF}{put original references, not Slipids param. paper.} & 64.3  &  303    \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{Area per lipid (APL) from different models of POPC with no ions\label{tab:apls_si} }
  \begin{tabular}{l|c c}
    model          & APL (\AA$^2$)   & Temperature [K] \\
    \hline
    Lipid14                   & 65.1$\pm$ 0.6  &  300 \\
    Lipid14 \cite{dickson14}  & 65.6$\pm$ 0.5  &  303 \\
    \hline
    ECC-lipids &        &  \\
    %Lipid14ecc0.80+sigma0.875 &        &  313    \\
    %($4.6\cdot 5.1 \, \mathrm{nm}^2$), 72 lipids patch, OPC3           & 63.2   &   313      \\
    ~ OPC3           & 62.2$\pm$ 0.6   &  300       \\
    ~ OPC3           & 64.2$\pm$ 0.6   &  313       \\
    ~ SPC/E          & 65.1$\pm$ 0.6   &  313       \\
    ~ OPC            & 64.4$\pm$ 0.6   &  313       \\
    ~ TIP4p/2005     & 66.8$\pm$ 0.6   &  313       \\
    %($9.2\cdot 10.2 \, \mathrm{nm}^2$), 288 lipids patch           & 65.5   &  313       \\ %% not done for this model with f_sigma=0.89
    %oMM small patch           & 63.65  &         \\
    %oMM 4xbig patch           & 63.7   &         \\
    \hline
    experiment   & 62.7  &  293    \\
    experiment \cite{jambeck12}\todoii{REF}{put original references, not Slipids param. paper.} & 64.3  &  303    \\
    experiment  & 67.3  &  323    \\
    experiment  & 68.1  &  333    \\
    %experiment POPE  & 56.6 &  303    \\
    \hline
  \end{tabular}
\end{table}
